---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

## Drink Purchase Analysis

This report explores data collected from a Google Form about drinks that people purchased. It analyses drink types, drink prices, and where drinks were purchased from, using **dynamic summaries** and **bar charts** that update automatically when new data is added.

```{r load-data}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRSFddzOLQ0P_l61-lFGnwQQbvRCShib-AZEmYme5754XTlyQ_wp1jCsJk8jgsHeHg8jP6e1nbB5F3y/pub?gid=778220564&single=true&output=csv") %>%
  rename(
    timestamp  = 1,
    drink_type = 2,
    cost_nzd   = 3,
    shop       = 4
  )
```

```{r summaries}
total_drinks <- logged_data$drink_type %>%
  length()

mean_price <- logged_data$cost_nzd %>%
  mean(na.rm = TRUE) %>%
  round(2)

min_price <- logged_data$cost_nzd %>%
  min(na.rm = TRUE) %>%
  round(2)

max_price <- logged_data$cost_nzd %>%
  max(na.rm = TRUE) %>%
  round(2)
```


::: dynamic-comment
A total of `r total_drinks` drink purchases have been recorded in this dataset. The average price paid was **$`r mean_price` NZD**, with the cheapest drink costing **$`r min_price`** and the most expensive costing **$`r max_price`**.
:::

---

```{r fig.width=8, fig.height=4}
logged_data %>%
  ggplot() +
  geom_bar(aes(x = drink_type, fill = drink_type)) +
  labs(
    title   = "Number of Drinks by Type",
    x       = "Drink Type",
    y       = "Count",
    caption = "Source: Drink Purchase Google Form"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

---

```{r price-groups}
price_groups <- logged_data %>%
  mutate(
    price_range = case_when(
      cost_nzd < 5                   ~ "Under $5",
      cost_nzd >= 5 & cost_nzd < 10  ~ "$5 to $9.99",
      cost_nzd >= 10                  ~ "$10 and over"
    )
  )
```

```{r fig.width=8, fig.height=4}
price_groups %>%
  ggplot() +
  geom_bar(aes(x = price_range, fill = price_range)) +
  labs(
    title   = "Number of Drinks by Price Range",
    x       = "Price Range",
    y       = "Count",
    caption = "Source: Drink Purchase Google Form"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

---

```{r fig.width=8, fig.height=5}
logged_data %>%
  ggplot() +
  geom_bar(aes(y = shop, fill = shop)) +
  labs(
    title   = "Number of Drinks Purchased by Shop",
    x       = "Count",
    y       = "Shop",
    caption = "Source: Drink Purchase Google Form"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

---

::: dynamic-comment
The `r total_drinks` drink purchases recorded show an average spend of $`r mean_price` NZD per drink. Prices range from $`r min_price` to $`r max_price`. The charts above show the breakdown of purchases by drink type, price range, and shop location.
:::

```{css, echo=FALSE}
body {
  font-family: Arial, sans-serif;
}
h2 {
  color: #2E86C1;
}
h3 {
  color: #117A65;
}
p {
  font-size: 16px;
}
```
